### 2015-10-20 weeklyReport/approach.tex
10-13-15,problem to return structured code examples
10-20, cluster code example

To identify methods that implement concerns, I build a prototype which invokes Code Search Engine (CSE) API and analyzes the results from CSE using partial program analysis~\cite{partialProgram:OOPSLA08}. I select SearchCode~\cite{SearchCode} because it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, with complete API documentations. To identify queried features in the returned source code,  I use the mean of TF-IDF weight  for each query term as a weighting factor and select top k (k=5) methods that are related to the given query.  This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location. I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program. TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.

>>>>

Our approach helps identify and integrate reusable examples in two phases:

\subsection{Example Collection Phase.}  
We identify the main features from multiple partial programs derived from informal resources. Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs and use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.

\noindent{\textbf{Query Code Search Engine.}}  We use code search engine SearchCode~\cite{SearchCode} to extract code examples based on free-form queries from users.  We choose it because 1) it has good support for free-form queries,  2) it is an open source code search engine with over 7000 projects from  Github, Bitbucket, Google Code, and Sourceforge, 3) it has complete API documentations and returns.

\noindent{\textbf{Locate Queried Features.}}  Considering that source code examples always contain multiple features, we identify program elements that are related to the queried features. I use the mean of TF-IDF weight  for each query term as a weighting factor and select all methods whose weighting score is bigger than a threshold.  This approach is similar to prior works that use  IR~\cite{Denys:FCA12} and NL analysis~\cite{Hill:FindConcept07} for feature location. I choose IR approach because other approaches require history or structural analysis that might not be feasible for partial program. TF-IDF =  $avg( \log (1 + f_{t,d}) \times  \log \frac {N} {n_t}), f_{t,d}$ is the frequency of term $t$ in method $d$, $N$ is the total number of methods, $n_t$ is the number of methods that have the term $t$.

\noindent{\textbf{Extract Structural Facts.}}  Before we extract structural facts, we construct symbol table for partial program based on the partial program analysis~\cite{partialProgram:OOPSLA08}.  We extract structural facts in an ontology instance. The ontology schema we use is the SEON Java ontology, which has been used in several prior works~\cite{gall:seonICSE10, Murphy:nlConcern11}.  Every extracted fact is represented in the ontology instance by one or more  \codefont{(subject, predicate, object)} triples. For instance, the fact that class $c_1$ extends class $c_2$ is represented by triple \codefont{($c_2$, subType, $c_1$)}. To manipulate the relationship between different facts, we use Resource Description Framework (RDF)  to represent each \codefont{(subject, predicate, object)} triple as an edge from \textit{subject} to \textit{object} labeled with {\it predicate}. We use \codefont{Apache Jena}, which is a Java framework for  linked data applications,  to create and process ontology instances. We define \codefont{subType} as  transitive predicate as ($c_1$, subType, $c_2$) and ($c_2$, subType, $c_3$) $\rightarrow$  ($c_1$, subType, $c_3$).

\begin{table}[ht]
\begin{center}
\caption{Structural Fact Types}
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}c|r|l@{}} \hline
Level&Type&Description\\\hline
&($c_1$, subType, $c_2$)& class $c_1$ extends $c_2$ \\
class&($c_1$, innerclass, $c_2$)& class $c_1$ has an inner class $c_2$ \\
level&($c$, field, $v$)& class $c$ has field $v$ \\ 
&($c$, method, $m$)& class $c$ contains method $m$ \\ \hline
&($m$, parameter, $v$)& method  $m$ has parameter $v$ \\ 
method&($m$, return, $t$)& method  $m$ returns an object of type $t$ \\ 
level&($e_1$, accesses, $e_1$)& $e_1$ = $e_2$, $e_1$ and $e_2$ are expressions\\ 
&($m_1$, call, $m_2$)& method  $m_1$ calls method $m_2$ \\ 
&($m$, variable, $v$)& method  $m$ has variable $m_2$ \\  \hline
&($o$, name, $s$)& The name of object  $o$ is  $s$ \\  \hline
\end{tabular*}
 \label{tab:dataset}
}
 \end{center}
\end{table}

\begin{figure}[!htb]
    \begin{minipage}{0.5\textwidth}
    \centering
\includegraphics[width=1\textwidth]{fig/rdf.pdf}
 \end{minipage}%
   \caption{RDF graph}
 \label{fig:rdf}
   \end{figure}

%The Resource Description Framework (RDF) [26] is the data-model for representing meta-data in the Semantic Web. The RDF data-model formalizes meta-data based on subject ? predicate ? object triples, so called RDF statements.

\subsection{Example Clustering Phase.}

We take three steps in this phase. Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts and API calls (i.e.,  \codefont{call} facts) to reduce the duplicated code snippets. Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements. Finally, we group auxiliary features based on program slicing and lexical similarity.

\noindent{\textbf{Cluster Examples.}}   We greedily select the most suitable structural correspondence~\cite{Cottrell:jigsaw08} and propagate the similarity of {\it object} nodes to the {\it subject} node.

 The comparison is done by investigating the lexical similarity and similar paths in RDF graphs. For example, when comparing UndoAction.actionPerformed() in Figure~\ref{fig:cluster1} (A), we first try to match the fact \codefont{(actionPerformed, calls, CompoundUndoManager. undo())}. We only look at the facts with the same type. We find  the fact  \codefont{(actionPerformed, calls, TextUndoManager.undo())} which is lexically similar though not identical to the target fact. We calculate the similarity score as follows: 1) We split the name for each element in the tuple by camel-case splitter and separators such as `.' and `('. Thus \codefont{TextUndoManager.undo()} is split as \codefont{[Text, Undo, Manager, undo]}.  2) We calculate the distance for each element as the $ editDistance(s_1,s_2)/ Min$ $(|s_1|, |s_2|)$, thus the similarity score between \codefont{TextUndoManager.undo()} and \codefont{CompoundUndoManager.undo()} is 0.25. 3) The distance between two tuples are the average distance for three elements. Thus the distance of two facts are 0.08.   We select  the most similar  fact by minimizing the similarity distance and we identify \codefont{(actionPerformed, calls, CompoundUndoManager.undo())} as the structural correspondence of the fact \codefont{(actionPerformed, calls, TextUndoManager.undo())}.

 Next, we try to match the fact   \codefont{(actionPerformed, calls, updateUndoState())}. Knowing that there is an edge from \codefont{updateUndoState()} to \codefont{setEnabled(undo.canUndo()} in RDF graph, we recursively match the fact \codefont{(updateUndoState, calls, setEnabled(undo.canUndo()))}  with  \codefont{(actionPerformed, calls, setEnabled(undo.canUndo()))}. The similarity score of {\it object} node \codefont{(updateUndoState, calls, setEnabled(undo.can Undo()))} is propagated to {\it subject} node \codefont{(actionPerformed, calls, updateUndoState())} as 0.4 compared to fact  \codefont{(actionPerformed, calls, setEnabled(undo. canUndo()))} in class \codefont{UndoAction}.  Our tool keeps on performing this matching until all facts in the target (Figure~\ref{fig:cluster1} (A)) is assigned a similarity score as 0 (i.e., fail to find correspondence) or a similarity score with other facts in the compared node.

Finally, the examples are clustered based on the number of  {\it object} nodes (without outer edge).  Our tool keeps on refining the large cluster to present a structured code examples to developers.

\noindent{\textbf{Extract Example Skeleton.}}  We extract all matched {\it object} nodes (without outer edge) and use them as  match seeds. We then perform dependency analysis to  extract example skeleton.  An example skeleton should start from an element without any inner edge and end at an element without any outer edge which covers all match seeds.

When selecting features, we use three rules to rank features in different examples: 1) the cost of reuse; 2) the number of resolved relationship; 3) the frequency of the feature in multiple examples; 4) the simplicity of code implementation.

The cost of reuse is measured as the number of outer edges in RDF graph, i.e., the more outer edges in RDF graph, the more expensive to reuse because it has more dependencies. We have rule 2) because  some of the relationships can not be resolved in partial program. When user tries to reuse the example, they have to manually resolve these external relationships. For instance, in Figure~\ref{fig:cluster2} (D), the feature group B.1 (\codefont{mUndoAction = new LintEditAction(undoAction, getEditorDelegate().getEditor())}) is not selected because the class \codefont{LintEditAction} cannot be resolved based on this partial program. The first two rules ease the reusability of our suggested code example. The third rule makes sure that the feature is representative and the last rule improves the understandability of our results. The simplicity is measured as the length of the code. For instance, we prefer \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, undo)} in Figure~\ref{fig:cluster24} (D) than \codefont{actionBars.setGlobalActionHandler (ITextEditorActionConstants.UNDO, getAction((ITextEditor) part,  ITextEditorActionConstants.UNDO))} because the former one is easier to interpret.

\noindent{\textbf{Group Auxiliary Features.}}    The auxiliary features are different example  skeletons.  (TBD)

\noindent{\textbf{Enable User Interaction.}}    The user could select the features and our tool is able to extract related elements based on their selection. (TBD)

%\begin{table}[ht]
%\begin{center}
%\caption{Common Structural Facts Extracted from the Examples }
%\label{tab:total}
%\vspace{1mm}
%\scriptsize{
%\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
%Level&Structural Facts\\\hline
%class&subType(Undo*Action, AbstractAction), \\ 
%&subType(Redo*Action, AbstractAction), \\ \hline
%method&override(actionPerformed(), Undo*Action, AbstractAction), \\
%&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
%statement&init(*,javax.swing.undo.UndoManager), \\
%&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
%& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
%\end{tabular*}
% \label{tab:dataset}
%
%We simplify some full names due to space limitation: 
%
%AbstractAction: javax.swing.AbstractAction;
%
%UndoListener: javax.swing.event.UndoableEditListener
%
%actionPerformed():actionPerformed(ActionEvent)
%}
% \end{center}
%\end{table}

### 2015-10-20 weeklyReport/motivating.tex
10-20, cluster code example

\input{example-scenario}
%\section{Motivating Example}
\section{Usage Scenario}
\noindent{\textbf{Add undo and redo action for TextEditor.}}

\begin{table}[ht]
\begin{center}
\caption{Search Result from Code Search Engine}
\label{tab:total}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}c|llrr@{}} \hline
No.&Name&Project&LOC&\# M\\\hline
1&TextEditor&textmash&1270&12\\
2,3&AndroidTextEditor&android&576&9\\
4&DocumentUndoManagerImpl&ide&1227&17\\
5,6,8&ConsoleTextEditor&groovy&321&7\\ 
7&PapyrusCDTEditor&eclipse.papyrus&393&7\\
9,10&AspectEditorContributor&eclipse&88&2\\ \hline
\end{tabular*}
 \label{tab:undoResult}
 \textbf{ \# M} represents the number of methods that contain the query terms. 
 {\bf No.} represents the rank from CSE. Note that CSE may return the same results for multiple times, as the same file may exist in multiple branches. For instance, we regard 5,6,8 as identical with manual inspection.

}
 \end{center}
\end{table}

To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}. Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}. Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.  Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE. We find that all code examples require multiple methods and classes to implement a feature. We also find that all code examples include other auxiliary features that are not directed related to the undo and redo feature.

We assume that user provides a seed code example for the reuse task. She selects the first result from CSE. She uses keyword search to locate undo and redo feature in 6 methods and regards them as  seed API calls. Shown in Figure~\ref{fig:undoEditor}, she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task. She recognizes that she needs to implement an \codefont{UndoAction} and \codefont{RedoAction} which are the subclass of \codefont{AbstractAction}, and overrides their actionPerform() method. In the actionPerformed() methods, she should invokes the \codefont{CompoundUndoManager.undo()} and  \codefont{CompoundUndoManager.redo()} correspondingly. Without knowing anything about \codefont{CompoundUndoManager}, she has to query CSE again for `CompoundUndoManager textmash'. This class consists of 17 methods (221 LOC) and she has to repeat to keyword search again to locate undo and redo feature in this class. With manual inspection, she notices that this \codefont{CompoundUndoManager} is a subclass of \codefont{javax.swing.UndoManager} and it overrides four methods \{\codefont{canUndo, canRedo, undo, redo}\} that are related to the feature. She notices that she actually does not need this \codefont{CompoundUndoManager} and decides to invoke its parent class \codefont{UndoManager}  instead. She also notices that she does not need the \codefont{CannotRedoException} by using \codefont{UndoManager}.

After she integrates \codefont{UndoManager, UndoAction, and RedoAction} to her context, she tests it and it fails to perform the feature. She has to look at other examples, and she finds the No.5 example returned from CSE.  This example seems promising because it is also an implementation of a TextEditor. She notice that  the API \codefont{doc.addUndoableEditListener (undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.

@@

\section{Problem 3}
Problem: During copy/paste based reuse, developers must remove irrelevant parts and find salient API elements based on the context.

Hypothesis: Our hypothesis is that having multiple examples of the same kind will help winnow out irrelevant parts, i.e, clustering multiple examples of the same kind and finding the commonality may help remove irrelevant parts.

@@

\begin{comment}
\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example. Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.  Our tool starts from the first cluster as it has the highest relative occurrence out of all examples. Based on partial program analysis, we generate a list of type facts to infer types and bind methods.

The common facts our tool extracts include: 
\begin{table}[ht]
\begin{center}
\caption{Common Structural Facts Extracted from the Examples }
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
Level&Structural Facts\\\hline
class&subType(Undo*Action, AbstractAction), \\ 
&subType(Redo*Action, AbstractAction), \\
&subType(*Listener, UndoListener)\\ \hline
method&override(actionPerformed(), Undo*Action, AbstractAction), \\
&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
statement&init(*,javax.swing.undo.UndoManager), \\
&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
\end{tabular*}
 \label{tab:dataset}

We simplify some full names due to space limitation:

AbstractAction: javax.swing.AbstractAction;

UndoListener: javax.swing.event.UndoableEditListener

actionPerformed():actionPerformed(ActionEvent)
}
 \end{center}
\end{table}

\noindent{\textbf{Example clustering phase.}} After extracting facts for each example, our tool identifies main facts shared in all 5 examples shown in Figure~\ref{fig:fact} part A. It leverages slicing to group related facts. In this example, 3 of them add \codefont{Undo*Action} to \codefont{JMenuItem} by invoking \codefont{JMenuItem.add (ActionEvent)} and support undo and redo actions for Text Editor shown in Figure~\ref{fig:fact} part B. The other two of them invoke \codefont{JButton.addActionListener(ActionEvent)} to add these two actions to \codefont{JButton}, and support \codefont{JApplet} Shape drawing shown in Figure~\ref{fig:fact} part C. After extracting both main facts and related facts, we generate two reuse tasks by combining main facts with each related fact group.

\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.  If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples. Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet. 
After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E. 
\end{comment}

>>>>

   \input{example-scenario}%\section{Motivating Example}
\section{Usage Scenario}
 To further illustrate that reuse task involves in multiple methods and classes, and the reuse task is hard without tool support, I imagine a scenario that user wants to add undo and redo actions for her Java Swing text editor application with undo/redo buttons, inspired by the evaluation task used in~\cite{Murphy:nlConcern11}.

\noindent{\textbf{Query: undo redo TextEditor}}

\begin{table*}[ht]
\begin{center}
\caption{Search Result from Code Search Engine}
\label{tab:total}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}c|rrrrrl@{}} \hline
No.&Name&Project&LOC&\#M&\#C&Involved objects and API calls\\\hline
1&TextEditor&textmash&1271&12&1&UndoManager, UndoAction, RedoAction\\
4&ConsoleTextEditor&groovy-core&322&7&1&UndoManager, UndoAction, RedoAction\\ \hline
2&AndroidTextEditor&android-sdk&587&9&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\
8&LayoutCanvas&sdk&1721&3&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\
9&IUEditorContributor&buckminster&193&2&2& IActionBars.setGlobalActionHandler(), ActionFactory.UNDO, ActionFactory.REDO\\ \hline
5&PapyrusCDTEditor&papyrus&393&7&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\
6&AspectEditorContributor&eclipse-plugin&89&2&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\
10&WSDLContributor&eclipse&254&2&4&IActionBars.setGlobalActionHandler(), ITextEditorActionConstants.UNDO\\ \hline
3&DocumentUndoImpl&ide&1228&17&3&FileDocumentUndoManager\\ \hline
7&ATETextPane&antlrworks&650&7&5&AbstractUndoableEdit.undo(), AbstractUndoableEdit.redo(),\\\hline
\end{tabular*}
 \label{tab:undoResult}
  {\bf No.} represents the rank from CSE. 
 \textbf{ \#M} represents the number of methods that contain the query terms.  \textbf{ \#C} represents the number of clusters the example belongs to.
}
 \end{center}
\end{table*}

 Without knowing any APIs, developer  first queries code search engine (CSE) with a free-form query \codefont{`undo redo TextEditor'}. %Figure~\ref{fig:undoEditor} illustrates the implementation of `add undo/redo' concern mentioned in~\cite{Murphy:nlConcern11} and blue part represents source code that implements this feature.  
Table~\ref{tab:undoResult} shows top 10 results returned from SearchCode CSE. %We find that all code examples require multiple methods and classes to implement a feature. We also find that all code examples include other auxiliary features that are not directed related to the undo and redo feature.

Before using our tool, she has to manually investigate all code search examples to identify which API calls are frequently used. She selects the first result from CSE and uses keyword search to locate undo and redo feature in 6 methods and regards them as search seed. She started to explore the relationships between these methods.  Shown in Figure~\ref{fig:cluster1} (A), she removes  the other  11 methods (865 LOC) that she regards as irrelevant to her reuse task. She recognizes that she needs to implement an \codefont{UndoAction} and \codefont{RedoAction} which are the subclass of \codefont{AbstractAction}, and overrides their actionPerform() method. In the actionPerformed() methods, she should invokes the \codefont{CompoundUndoManager.undo()} and  \codefont{CompoundUndoManager.redo()} correspondingly. Without knowing anything about \codefont{CompoundUndoManager}, she has to query CSE again for `CompoundUndoManager textmash'. This class consists of 17 methods (221 LOC) and she has to repeat to keyword search again to locate undo and redo feature in this class. With manual inspection, she notices that this \codefont{CompoundUndoManager} is a subclass of \codefont{javax.swing.UndoManager} and it overrides four methods \{\codefont{canUndo, canRedo, undo, redo}\} that are related to the feature. She notices that she actually does not need this \codefont{CompoundUndoManager} and decides to invoke its parent class \codefont{UndoManager}  instead. She also notices that she does not need the \codefont{CannotRedoException} by using \codefont{UndoManager}.

After she integrates \codefont{UndoManager, UndoAction, and RedoAction} to her context, she tests it and it fails to perform the feature. She has to look at other examples, and she finds the fifth example from CSE is similar to the first example.  Shown in Figure~\ref{fig:cluster1} (B), This example seems similar because it uses an \codefont{TextUndoManager}, and implements \codefont{UndoAction} and \codefont{RedoAction}. She notice that  the API \codefont{doc.addUndoable EditListener(undoManager)} seems the one that she misses now, but again, she has to investigate the class   \codefont{TextUndoManager} again.

@@

 Our tool is able to represent code examples returned from CSE in a structured manner. We cluster the examples that share similar API calls and extract the queried features. Shown in Figure~\ref{fig:cluster1} (C), our tool extracts a skeleton of reuse code example for the queried feature. At the same time, we group auxiliary features based on program slicing and lexical similarity so that the user can select the features that she wants, as shown in Figure~\ref{fig:cluster1} (D).

@@

%\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.  If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples. Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet. After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E.

### 2015-10-20 weeklyReport/problem.tex
10-20, cluster code example

Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

Both location and integration of reusable examples are not trivial. For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.  As a result, developers always query general search engines like Google or expert sites like StackOverflow to investigate potential tutorials for desired features. These search engines will return a list of informal documentations and users have to search for source code elements in these resources. Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}. Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls). For the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context. Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers. The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.  Moreover,  the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.

To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature. We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples. 
Figure~\ref{fig:system} illustrates the process of our system. 
Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.

@@

Our approach helps identify and integrate reusable examples in three phases:
\begin{itemize}
\item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources. Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}. We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.

\item \textbf{Example Clustering Phase.} We take three steps in this phase. Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts to reduce the duplicated code snippets. Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements. We ignore the specific related elements that appear in a single example. Finally, we group the related elements based on their common interaction with main elements.

\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context. After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context. 
\end{itemize}

 \begin{figure*}[!htb]
    \centering
\includegraphics[width=1\textwidth]{fig/system.pdf}
       \caption{System process overview}
        \label{fig:system}
   \end{figure*}

>>>>

Problem: The code examples returned from code search engine or other code search tools are not structured.

%Reuse tasks involve multiple related classes and methods, yet code search engines do not help developers recognize the latent structure among related classes/methods.

%Hypothesis: We can find and rank related elements by following the structural dependencies of seed API elements in code.

Input: a set of code examples returned from code search engine.

Output: a list of code example clusters organized based on their structural similarity.

%Sub questions: Do reuse tasks involve multiple related classes and methods? Can existing tools find reusable examples that involve multiple related classes and methods?

%To answer these two subquestions, I search for the evaluation dataset for existing feature location/concern mining tools~\cite{Denys:FCA12, Hill:FindConcept07, Hassan:concernHistory10, Breu:DynamicAspect04} shown in Table~\ref{tab:concern},    reuse tools~\cite{Holmes:reuse07, Holmes:ASE09} shown in Table~\ref{tab:reuse}, and code search tools using free-form query ~\cite{sniff:Sen09, Portfolio:DenysICSE11, Sourcerer:SC14, Gvero:ICSE15, spotWork:ICSE14} shown in Table~\ref{tab:freeform}. We find that most medium-scale or large-scale reuse tasks involve multiple methods and classes,  and the developer should implement multiple methods and classes to finish the reuse task. Existing  code completion tools can complete a single method which involves in multiple API calls, yet they assume that all related APIs or  objects used in their suggested code snippet already exist. We argue that this assumption might not hold for a non-trivial reuse task, because developers need to implement the salient API calls that provide the main functionality as well as other related elements based on the latent structure.

%Developers frequently use source code examples as the basis for interacting with an  application programming interface (API) to obtain the needed functionality~\cite{CodeSearch:FSE15}.  In this case, the source code example serves as the explicit origin for a reuse task which transforms a sequence of APIs with corresponding control structure to the target context~\cite{Frakes:reuseStatus05}.  During the process of reuse task such as `add undo and redo actions in my Graphics Editor', developers often query for a set of examples considering the task, and integrate examples that match the task into their system~\cite{Parsons:cognitiveReuse04}.

%Both location and integration of reusable examples are not trivial. For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.  As a result, developers always query general search engines like Google or expert sites like StackOverflow to investigate potential tutorials for desired features. These search engines will return a list of informal documentations and users have to search for source code elements in these resources. Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}. Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls). For the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context. Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers. The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.  Moreover,  the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.

%To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature. We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples.  Figure~\ref{fig:system} illustrates the process of our system.  Given a free-form query from users, our tool invokes code search engine  to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.

@@

%\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context. After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context.

% \begin{figure*}[!htb]
%    \centering
%\includegraphics[width=1\textwidth]{fig/system.pdf}
%       \caption{System process overview}
%        \label{fig:system}
%   \end{figure*}
